---
title: "The title"
author:
- name: First Author
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: my@email.com
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Ernst-August Doelle
  affiliation: '1,2'
  role: Writing - Review & Editing
shorttitle: Title
output:
  html_document:
    df_print: paged
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
keywords: keywords
wordcount: X
bibliography: r-references.bib
toc: yes
toc_float: yes
floatsintext: no
figurelist: no
tablelist: no
footnotelist: no
linenumbers: no
mask: no
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Wilhelm-Wundt-University
- id: '2'
  institution: Konstanz Business School
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Citations in papaja, detele appropriately later

Add the bibtex entry in the .bib file. You can find the entries in Google scholar, 
but double check since it is not always correct. 

Call the citations in the text:

Citation within parentheses	[@R-papaja]

Multiple citations	[@R-papaja; @R-base]

In-text citations	@R-papaja

Year only	[-@R-base]

Only if your citation appears in the text it will also show up in the Reference 
list. Don't manually modify the Reference list.

## Executive Summary 

(150 words) – 0.3 POINTS
Summarize the report. Write this as the very last thing.

What is the main topic you are addressing?

what are your research questions and hypotheses?  

what are your results and the main conclusion?



## Introduction 
### Main topic
In this paper, we are going to study the presence of social networks within a movie streaming platform. We're focusing on the structure of links among a group of social players, which consist of users watching and rating movies on Netflix.  
Users of Netflix's movie recommendation algorithms are frequently given specific questions about their interests for certain items (which they provide by liking or disliking them, for example). These choices are then immediately integrated into the underlying learning system for future suggestions. If a recommender system starts promoting unwanted products after incorporating new preferences, the user may try to steer the system in the future by correcting it or supplying alternate preference information. 

### Importance
It is important to study the presence of these socials networks because this could potentially improve the recommender engine that this currently in place. For example, if you know that a user is likely to like a movie that other users with the same “liking profile” also like, you can recommend that movie to the user. When these connections are studied thoroughly, you could have a high probability that the recommendation is successful. This could have a large impact on a movie streaming platform. 

### Existing studies
In this paper, we will be looking into the Netflix Price Dataset. In 2006 Netflix decided to start a competition with a grand prize of 1 million US dollars. The goal of the competition was to create a collaborative filtering algorithm to predict user ratings for films, based on previous ratings without any other information about the users or films. In order to win you had to at least improve on Netflix's own algorithm by 10%. 
During the competition a lot of literature has emerged about the dataset and the competition. [@bell2007lessons; @takacs2008matrix; @narayanan2006break] 

However, no papers or any other literature can be found on network analysis on this dataset. We like to fill this gap in the literature by analysing the network and network structure that arises from the subset of the data that we will use. 
[@guillory2011simultaneous] developed an active movie recommendation system for Netflix. They found that a recommender system should not constantly ask questions to a user, because those reduces the user's mental image of how the recommendation system learns, prompting some participants to "lose track of what they were teaching". According to @amershi2014power, this was because users are not always eager to act as simple oracles (repeatedly telling the recommendation system whether they like something or not). This is interesting to take into account for our research, because this would mean that a social network within a movie recommendation system can never be fully exposed. 

### Questions and hypotheses
In this dataset, we can easily see connections between users and movies, but not between just the users or just the movies. At least not, when we do not include one or the other. 

## Methodology

### Dataset 
(about 500 words) 1 POINT (+ BONUS)
*	Which data set are you going to use? Three options:

o	Use readily/easily available data (0 bonus points)

o	Combine two or more existing datasets (max 0.5 bonus points)

o	Scrape or collect your own data (max. 1 bonus point)

*	Clearly explain where the data is coming from:

o	Who collected the data?

o	What is the source?

o	When was the data produced?

o	How was the data collected?

*	Provide descriptive measures of your data (tables, plots, etc.)

*	Why is this data useful to study your topic and answer your research questions?

*	What is the potential bias in the data? How does this affect your results?

### Data analysis (Research Rationale)
(about 500 words) – 1 POINTS
*	Why are these two methods suitable for your data?

*	Why are these two methods suitable for your research questions?

*	Are there other methods to address these questions? If yes, why are the 
methods you chose better for this case?



## Results
(about 2000 words)

### Model 1
(about 1000 words) – 2.5 POINTS

*	Present your results appropriately (plots, tables…) and discuss your findings 
in plain English

*	Discuss the meaning of your findings in relation to your hypothesis. (half of
the points evaluated in this other part)


```{r echo = FALSE, results = 'asis'}
# table example
cn <- c("age", "gender", "eyes_col")
one <- c(7, "M", "BLUE")
two <- c(8, "F", "BROWN")
three <- c(8, "M", "GREEN")
four <- c(7, "F", "PINK")

tab <- rbind(cn, one, two, three, four)
rownames(tab) <- NULL
knitr::kable(tab)
```


### ERGM 
(about 1000) – 2.5 POINTS


* Present your results appropriately (plots, tables…) and discuss your findings 
in plain English

* Discuss the meaning of your findings in relation to your hypothesis. (half of 
the points evaluated in this other part)

Option 1: 

```{r model 1, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(lm.D9))


```

Option 2

```{r model 2, echo = FALSE, results = 'asis'}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(list(lm.D9, lm.D90)))


```


Option 3

```{r model 3, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")


texreg::plotreg(lm.D9)


```


Option 4

```{r model 4, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

texreg::plotreg(list(lm.D9, lm.D90))

```


## Conclusion

(about 350 words) – 0.7 POINTS
What were your topic and research questions again? (1 sentence)

What did you learn from the two analysis you run? *** most important point to 
address 0.5 POINTS here

Who benefits from your findings?

What does remain an open problem?

Can you give suggestions for future work in this area?



\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
